---
title: "Does Spotify know me?"
author: "Silva Patrick"
format: 
  revealjs:
    width: 1300
    min-scale: 1
    margin: 0.05
    smaller: true
    show-slide-number: "all"
---

```{r include=FALSE}
renv::activate()
```

```{r include=FALSE, echo=FALSE}
library(tidyverse)
library(spotifyr)
library(ggradar)
library(grid)
library(gridExtra)
```

```{r include=FALSE, echo=FALSE}
theme_set(theme_minimal(base_size = 14))

artists_af <- read_csv("data/top_artists_with_audio_features.csv")
hist2023 <- read.csv("data/Streaming_History_2023.csv")
raw <- read.csv("data/Streaming_2023_Raw.csv")

artists_genre <- artists_af |>
  select(artist_name, genres) |>
  distinct()

data <- hist2023 |>
  filter(master_metadata_album_artist_name %in% pull(artists_genre, artist_name)) |>
  left_join(artists_genre, 
            by = join_by(master_metadata_album_artist_name == artist_name),
            multiple = "all")

top_genres <- data |>
  count(genres, sort = TRUE) |>
  head(10) |>
  pull(genres)

platform_colors <- c("android" = "#A4C639", "windows" = "#3778BF",
                     "ios" = "#7D7D7D", "osx" = "#A6109F")
titles_theme <- theme(plot.title = element_text(size = 18, hjust = 0.5, 
                                                face = "bold"),
                      plot.subtitle = element_text(size = 13, hjust = 0.5))
```

# Some Extra Information About the Data

In the data I got from Spotify, we can find more than only my listening activity. We can find:

-   Payment details (Card number, Owner name, Owner address)

-   Devices used (version of device included) + IP address (trace back to Luxembourg)

-   Advertisement groups I was put in. Here are some:

    -   1P_Custom_Auto_Hyundai \[Advertiser-Specific\]

    -   1P_Custom_Samsung_Galaxy_A_Series_Users \[Advertiser-Restricted\]

    -   1P_Custom_Disney_Marvel_Playlist_Streamers

These information is just listed inside the many JSON files they gave me so I created no plots about them but I wanted to share this as I think this adds some weight into what I want to convey with the created plots.

------------------------------------------------------------------------

```{r}
hist2023 |>
  mutate(month = month(date, label = TRUE)) |>
  count(month, platform) |>
  ggplot(aes(x = month, y = n, fill = platform)) +
  geom_col() +
  scale_fill_manual(values = platform_colors) +
  labs(title = "Number of streams during each month of 2023",
       subtitle = "Data goes until the 7th December 2023",
       y = element_blank(),
       x = element_blank()) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  titles_theme
```

------------------------------------------------------------------------

```{r}
hist2023 |>
  mutate(month = month(date),
         day = day(date),
         wday = wday(date, label = TRUE),
         hour = hour(hms(time))) |>
  filter(month == 11 & day <= 25 & day >= 12) |>
  mutate(week = ifelse(day <= 18, "Week of the 12/11 - 18/11",
                       "Week of the 19/11 - 25/11")) |>
  group_by(week) |>
  ggplot(aes(x = hour, y = fct_rev(wday), colour = platform)) +
  geom_point(aes(size = 8)) +
  scale_color_manual(values = platform_colors) +
  labs(title = "When and on what did I use Spotify?",
       y = element_blank(),
       x = element_blank()) +
  theme(legend.position = "bottom",
        legend.title = element_blank()) + 
  scale_x_continuous(breaks = seq(0, 23, 1)) +
  titles_theme +
  facet_wrap(~week, ncol = 1) +
  guides(size = "none")
```

------------------------------------------------------------------------

```{r}
hist2023 |>
  mutate(month = month(date),
         day = day(date),
         wday = wday(date, label = TRUE),
         hour = hour(hms(time))) |>
  filter(month == 11 & day <= 25 & day >= 12) |>
  mutate(week = ifelse(day <= 18, "Week of the 12/11 - 18/11",
                       "Week of the 19/11 - 25/11")) |>
  group_by(week) |>
  ggplot(aes(x = hour, y = fct_rev(wday), colour = platform)) +
  geom_point(aes(size = 8)) +
  scale_color_manual(values = platform_colors) +
  labs(title = "When and on what did I use Spotify?",
       y = element_blank(),
       x = element_blank()) +
  theme(legend.position = "bottom",
        legend.title = element_blank()) + 
  scale_x_continuous(breaks = seq(0, 23, 1)) +
  titles_theme +
  facet_wrap(~week, ncol = 1) +
  annotate("rect", xmin = c(8,10,9,8,10), xmax = c(14,16,16,13,14),
           ymin = c("Mon","Tue","Wed","Thu","Fri"), 
           ymax = c("Mon","Tue","Wed","Thu","Fri"), 
           alpha = 1, color = "red", fill = "red") +
  guides(size = "none")
```

------------------------------------------------------------------------

```{r}
data |>
  filter(genres %in% top_genres) |>
  ggplot(aes(y = fct_rev(fct_infreq(genres)), fill = genres)) +
  geom_bar() +
  labs(title = "Genres I listened to most in 2023",
       subtitle = "(and their count)",
       y = element_blank(),
       x = element_blank()) +
  scale_fill_manual(values=c("j-rock"="red", "rock"="red",
                             "alternative rock" = "red")) +
  theme(legend.position = "none") +
  titles_theme
```

# Genres

To inquire this incident, let's look at the average audio features of the discography of some artists that have been tagged with these genres and see if we can find any relations.

In the Spotify data, genres are stored in artists only. Not in songs.

------------------------------------------------------------------------

```{r}
artists_af |>
  filter(artist_name == "Cocteau Twins") |>
  select(album_name, danceability, energy, mode, speechiness, acousticness,
         instrumentalness, liveness, valence) |>
  group_by(album_name) |>
  summarize(across(everything(), list(mean = mean))) |>
  ggradar(plot.legend = FALSE, 
          fill = TRUE, fill.alpha = 1,
          values.radar = element_blank(),
          group.point.size = 0,
          axis.labels = c('', '', '' , '', '', '', '', ''),
          plot.extent.x.sf = 1,
          plot.extent.y.sf = 1,
          group.line.width = 1,
          group.colours = (c("Victorialand" = "#e78558",
                             "The Moon and the Melodies" = "#e78558",
                             "Garlands" = "#e78558",
                             "Head Over Heels" = "#e78558"))) +
  facet_wrap(~album_name, ncol = 5) + 
  theme(strip.background = element_blank(),
       strip.text.x = element_blank()) +
  labs(title = "Cocteau Twins (Alt. Rock)") +
  titles_theme
```

------------------------------------------------------------------------

```{r}
artists_af |>
  filter(artist_name == "Talking Heads") |>
  filter(str_detect(album_name, "Deluxe", negate = TRUE)) |>
  filter(str_detect(album_name, "Expanded", negate = TRUE)) |>
  select(album_name, danceability, energy, mode, speechiness, acousticness,
         instrumentalness, liveness, valence) |>
  group_by(album_name) |>
  summarize(across(everything(), list(mean = mean))) |>
  ggradar(plot.legend = FALSE, 
          fill = TRUE, fill.alpha = 1,
          values.radar = element_blank(),
          group.point.size = 0,
          axis.labels = c('', '', '' , '', '', '', '', ''),
          plot.extent.x.sf = 1,
          plot.extent.y.sf = 1,
          group.line.width = 1,
          group.colours = (c("Stop Making Sense (Live)" = "#e78558"))) +
  facet_wrap(~album_name, ncol = 5) + 
  theme(strip.background = element_blank(),
        strip.text.x = element_blank()) +
  labs(title = "Talking Heads (Alt. Rock & Rock)") +
  titles_theme
```

------------------------------------------------------------------------

```{r}
artists_af |>
  filter(artist_name == "The Beatles") |>
  filter(str_detect(album_name, "Deluxe", negate = TRUE)) |>
  filter(str_detect(album_name, "Live", negate = TRUE)) |>
  select(album_name, danceability, energy, mode, speechiness, acousticness,
         instrumentalness, liveness, valence) |>
  group_by(album_name) |>
  summarize(across(everything(), list(mean = mean))) |>
  ggradar(plot.legend = FALSE, 
          fill = TRUE, fill.alpha = 1,
          values.radar = element_blank(),
          group.point.size = 0,
          axis.labels = c('', '', '' , '', '', '', '', ''),
          plot.extent.x.sf = 1,
          plot.extent.y.sf = 1,
          group.line.width = 1,
          group.colours = (c("Yellow Submarine (Remastered)" = "#e78558"))) +
  facet_wrap(~album_name, ncol = 5) + 
  theme(strip.background = element_blank(),
        strip.text.x = element_blank()) +
  labs(title = "The Beatles (Rock)") +
  titles_theme
```

------------------------------------------------------------------------

```{r}
artists_af |>
  filter(artist_name == "Fishmans") |>
  select(album_name, danceability, energy, mode, speechiness, acousticness,
         instrumentalness, liveness, valence) |>
  group_by(album_name) |>
  summarize(across(everything(), list(mean = mean))) |>
  ggradar(plot.legend = FALSE, 
          fill = TRUE, fill.alpha = 1,
          values.radar = element_blank(),
          group.point.size = 0,
          axis.labels = c('', '', '' , '', '', '', '', ''),
          plot.extent.x.sf = 1,
          plot.extent.y.sf = 1,
          group.line.width = 1,
          group.colours = (c("LONG SEASON" = "#E9967A"))) +
  facet_wrap(~album_name, ncol = 5) + 
  theme(strip.background = element_blank(),
        strip.text.x = element_blank()) +
  labs(title = "Fishmans (J-Rock)") +
  titles_theme
```

------------------------------------------------------------------------

```{r}
artists_af |>
  filter(artist_name == "Kendrick Lamar") |>
  select(album_name, danceability, energy, mode, speechiness, acousticness,
         instrumentalness, liveness, valence) |>
  group_by(album_name) |>
  summarize(across(everything(), list(mean = mean))) |>
  ggradar(plot.legend = FALSE, 
          fill = TRUE, fill.alpha = 1,
          values.radar = element_blank(),
          group.point.size = 0,
          axis.labels = c('', '', '' , '', '', '', '', ''),
          plot.extent.x.sf = 1,
          plot.extent.y.sf = 1,
          group.line.width = 1,
          group.colours = (c("#E9967A"))) +
  facet_wrap(~album_name, ncol = 5) + 
  theme(strip.background = element_blank(),
        strip.text.x = element_blank()) +
  labs(title = "Kendrick Lamar (Hiphop)") +
  titles_theme
```

# Conclusion

So, for me it's easy to recognize all my patterns inside of my Spotify data. However, with all the data to have it's not impossible to get an average idea of my schedule.

Unlike this idea suggest, the song data they share seems to be a bit messy.

# Questions?
