```{r}
library(spotifyr)
library(tidyverse)
library(lubridate)
library(httpuv)
library(viridis)
```

```{r}
Sys.setenv(SPOTIFY_CLIENT_ID = '50a6babd1746400f9de5a5a6ddf2b870')
Sys.setenv(SPOTIFY_CLIENT_SECRET = '290ce59c9b10458987bf608c2ee732bb')

authorization_code <- get_spotify_authorization_code(
                        scope = scopes()[c(4,7,8,9,10,14,15,17)])

data <- read_csv("data/lastfm_and_afs.csv") |>
  mutate(length = hms(length))
theme_set(theme_minimal(base_size = 14))
```

Audio Features: 

Beats Per Minute (BPM) - The tempo of the song.
Energy - The energy of a song - the higher the value, the more energtic the song
Danceability - The higher the value, the easier it is to dance to this song.
Loudness - The higher the value, the louder the song.
Valence - The higher the value, the more positive mood for the song.
Length - The duration of the song.
Acoustic - The higher the value the more acoustic the song is.
Popularity - The higher the value the more popular the song is.
A.Sep - maximizes the artist separation in the set (removed)
Rnd - A randon number. Sort by this column to shuffle your playlist. (removed)

```{r}
data |>
  select(- c("listen_date", "listen_time")) |>
  filter(!is.na(bpm)) |>
  distinct() |>
  ggplot(aes(x = energy, y = bpm, color = valence)) +
  geom_point() +
  scale_color_viridis()
```

```{r}
data |>
  select(- c("listen_date", "listen_time")) |>
  filter(!is.na(bpm)) |>
  distinct() |>
  ggplot(aes(x = energy, y = bpm, color = valence)) +
  geom_point() +
  scale_color_viridis()
```

```{r}
data |>
  filter(bpm == 0) |>
  select(artist, track, energy) |>
  distinct()
```

```{r}
data |>
  select(- c("listen_date", "listen_time")) |>
  filter(!is.na(bpm)) |>
  distinct() |>
  ggplot(aes(x = bpm, y = valence, color = energy)) +
  geom_point() +
  scale_color_viridis()
```

```{r}
data |>
  filter(valence == 0) |>
  select(artist, track, energy) |>
  distinct()
```

```{r}
data |>
  filter(!is.na(length)) |>
  group_by(artist, track, length) |>
  summarise(time_listened = sum(as.numeric(length)), .groups = "drop") |>
  mutate(time_listened = seconds_to_period(time_listened)) |>
  arrange(desc(time_listened))

data |>
  filter(!is.na(length)) |>
  group_by(artist, track, length) |>
  summarise(times_played = n(), .groups = "drop") |>
  mutate(time_listened = seconds_to_period(times_played * as.numeric(as.period(ms(length), unit = "sec")))) |>
  arrange(desc(time_listened)) |>
  relocate(artist, .after = time_listened) |>
  relocate(track, .after = time_listened)
```

```{r}
data |>
  filter(!is.na(length)) |>
  group_by(artist) |>
  summarise(time_listened = sum(as.numeric(length)), .groups = "drop") |>
  mutate(time_listened = seconds_to_period(time_listened)) |>
  arrange(desc(time_listened))
```

```{r}
data |>
  filter(!is.na(length)) |>
  group_by(artist, album) |>
  summarise(time_listened = sum(as.numeric(length)), .groups = "drop") |>
  mutate(time_listened = seconds_to_period(time_listened)) |>
  arrange(desc(time_listened))
```

```{r}
data |>
  filter(!is.na(bpm)) |>
  mutate(hour_listened = hour(listen_time)) |>
  # relocate(hour_listened) |>
  count(hour_listened, sort = TRUE) |>
  ggplot(aes(x = hour_listened, y = n)) +
  geom_col() +
  labs(title = "Streams per hour from 09/21 until 12/23", y = NULL, x = "Hour")
```

```{r}
data |>
  filter(!is.na(bpm)) |>
  filter(!(year(listen_date) == "2023" & month(listen_date) == "12")) |>
  filter(!(year(listen_date) == "2021" & month(listen_date) == "09")) |>
  mutate(hour_listened = hour(listen_time)) |>
  group_by(hour_listened) |>
  summarise(avg_energy = mean(energy),
            avg_valence = mean(valence),
            avg_bpm = mean(bpm),
            avg_danceability = mean(danceability),
            avg_loudness = mean(loudness),
            avg_acoustic = mean(acoustic),
            med_energy = median(energy),
            med_valence = median(valence),
            med_bpm = median(bpm),
            med_danceability = median(danceability),
            med_loudness = median(loudness),
            med_acoustic = median(acoustic),) |>
  # relocate(hour_listened) |>
  ggplot(aes(x = hour_listened)) +
  geom_line(aes(y = avg_energy, color = "avg_energy")) +
  geom_line(aes(y = avg_bpm, color = "avg_bpm")) +
  geom_line(aes(y = avg_valence, color = "avg_valence")) +
  #geom_line(aes(y = med_energy, color = "med_energy")) +
  #geom_line(aes(y = med_valence, color = "med_valence")) +
  #geom_line(aes(y = med_bpm, color = "med_bpm")) +
  geom_line(aes(y = avg_danceability, color = "avg_danceability")) +
  geom_line(aes(y = avg_loudness, color = "avg_loudness")) +
  geom_line(aes(y = avg_acoustic, color = "avg_acoustic")) +
  #geom_line(aes(y = med_danceability, color = "med_danceability")) +
  #geom_line(aes(y = med_loudness, color = "med_loudness")) +
  #geom_line(aes(y = med_acoustic, color = "med_acoustic")) +
  expand_limits(y = c(0, 120)) +
  labs(title = "Audio features in songs per hour from 10/21 until 11/23", y = NULL, x = "Hour")
```

Problem => not much can be interpreted because the time window is too big.

```{r}
data |>
  filter(!is.na(bpm)) |>
  filter((year(listen_date) == "2023" & month(listen_date) == "11")) |>
  mutate(hour_listened = hour(listen_time)) |>
  group_by(hour_listened) |>
  summarise(avg_energy = mean(energy),
            avg_valence = mean(valence),
            avg_bpm = mean(bpm),
            avg_danceability = mean(danceability),
            avg_loudness = mean(loudness),
            avg_acoustic = mean(acoustic),
            med_energy = median(energy),
            med_valence = median(valence),
            med_bpm = median(bpm),
            med_danceability = median(danceability),
            med_loudness = median(loudness),
            med_acoustic = median(acoustic),) |>
  # relocate(hour_listened) |>
  ggplot(aes(x = hour_listened)) +
  geom_line(aes(y = avg_energy, color = "avg_energy")) +
  geom_line(aes(y = avg_bpm, color = "avg_bpm")) +
  geom_line(aes(y = avg_valence, color = "avg_valence")) +
  #geom_line(aes(y = med_energy, color = "med_energy")) +
  #geom_line(aes(y = med_valence, color = "med_valence")) +
  #geom_line(aes(y = med_bpm, color = "med_bpm")) +
  geom_line(aes(y = avg_danceability, color = "avg_danceability")) +
  geom_line(aes(y = avg_loudness, color = "avg_loudness")) +
  geom_line(aes(y = avg_acoustic, color = "avg_acoustic")) +
  #geom_line(aes(y = med_danceability, color = "med_danceability")) +
  #geom_line(aes(y = med_loudness, color = "med_loudness")) +
  #geom_line(aes(y = med_acoustic, color = "med_acoustic")) +
  expand_limits(y = c(0, 120)) +
  labs(title = "Audio features in songs per hour from 11/23", y = NULL, x = "Hour")

data |>
  filter(!is.na(bpm)) |>
  filter((year(listen_date) == "2023" & month(listen_date) == "11")) |>
  mutate(hour_listened = hour(listen_time)) |>
  group_by(hour_listened) |>
  summarise(med_energy = median(energy),
            med_valence = median(valence),
            med_bpm = median(bpm),
            med_danceability = median(danceability),
            med_loudness = median(loudness),
            med_acoustic = median(acoustic),) |>
  # relocate(hour_listened) |>
  ggplot(aes(x = hour_listened)) +
  geom_line(aes(y = med_energy, color = "med_energy")) +
  geom_line(aes(y = med_valence, color = "med_valence")) +
  geom_line(aes(y = med_bpm, color = "med_bpm")) +
  geom_line(aes(y = med_danceability, color = "med_danceability")) +
  geom_line(aes(y = med_loudness, color = "med_loudness")) +
  geom_line(aes(y = med_acoustic, color = "med_acoustic")) +
  expand_limits(y = c(0, 120)) +
  labs(title = "Audio features in songs per hour from 11/23", y = NULL, x = "Hour")
  
```

-> pointless due to much passive listening. i listen to specific songs or artists, forget about the music
and listen what spotify recommends me. songs listened together with friends also change the output.



