```{r}
renv::install() 
```

Run only if there is a problem with renv.
```{r}
install.packages('spotifyr')
install.packages('tidyverse')
install.packages('lubridate')
install.packages("httpuv")
install.packages('ggplot2')
devtools::install_github("xl0418/ggradar2",dependencies=TRUE)
install.packages("viridis")

renv::snapshot()
renv::activate()
```

```{r}
library(spotifyr)
library(tidyverse)
library(lubridate)
library(httpuv)
```

I am not sure if this will work on your side because I had to confirm on my Spotify
I was accepting the use of the chosen scopes. So, maybe the connection on your side,
will not work.

I am not sure if the chunks using Spotify to authenticate will work on your side.
I also suggest not running these chunks because Artists on my top may change from
the moment this is written to the moment you run this.

```{r}
# my personal spotify account account
Sys.setenv(SPOTIFY_CLIENT_ID = '50a6babd1746400f9de5a5a6ddf2b870')
Sys.setenv(SPOTIFY_CLIENT_SECRET = '290ce59c9b10458987bf608c2ee732bb')

authorization_code <- get_spotify_authorization_code(scope = 
                                                    scopes()[c(4,7,8,9,10,14,15,17)])
```

Collect the artists I have been listening most the last 6 months.

```{r}
top_artists <- get_my_top_artists_or_tracks(type = "artists", limit = 50, 
                                            time_range = "medium_term",
                                            authorization = authorization_code)

top_artists <- top_artists |>
  distinct() |>
  select(genres, id, name, popularity) |>
  unnest(genres)

write_csv(top_artists, 
          file = "../data/top_artists.csv")
```

Collect the whole discography of these artists.

```{r} 
artist_ids <- top_artists |>
  select(id) |>
  distinct() |>
  pull(id)
audio_features <- get_artist_audio_features(artist_ids[1])
for (id in artist_ids[2:50]) {
  audio_features <- rbind(audio_features, get_artist_audio_features(id))
}

audio_features |>
  left_join(top_artists, by = join_by(artist_name == name)) |>
  select(artist_name, album_type, album_release_date, danceability, energy, key, loudness,
         mode, speechiness, acousticness, instrumentalness, liveness, valence, tempo, 
         time_signature, duration_ms, explicit, track_name, album_name, key_name, mode_name, 
         popularity, genres) |>
  write_csv(file = "../data/top_artists_with_audio_features.csv")
```
